A formalization of semi-simplicial and semi-cubical sets in dependent type theory

### 2023-01-15 paper/paper.tex
paper, paper.bib: polish, fix bib

\section{Our setting}
In this section,

\subsection{Working with sets in type theory}
Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}. It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}. Type theory is a flexible formalism supporting different models. One of this model interprets types as topological spaces, where equality is interpreted as path and substitutivity of equality as transport. This model supports the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}. In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number. Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of Boolean values, called $\textsf{bool}$, the type of natural numbers.

@@

\begin{enumerate}
  \item[(i)] UIP holds on the unit and bool type:

    \begin{align*}
      \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
      \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
      \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
    \end{align*}

  \item[(ii)] UIP propagates to $\Sigma$-types.
  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
\end{enumerate}

@@

\subsection{Intuition for our formal construction}
\begin{notation}[$\Sigma$]
  In the prose that follows, we assume the existence of $\Sigma$-types with projections $\hd$ and $\tl$.
\end{notation}

To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$. A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\filler$ is a filled $\framep$.

>>>>

\section{Our setting}
In this section, we explain how we recover the notion of sets in type theory, and briefly explain the difference between the fibered and indexed representations.

\subsection{Working with sets in type theory}
Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}. It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}. Type theory is a flexible formalism supporting different models. One of this model interprets types as topological spaces, where equality is interpreted as path and substitutivity of equality as transport. This model supports the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}. In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number. Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.

@@

\begin{enumerate}
  \item[(i)] UIP holds on the unit and bool type:
    \begin{align*}
      \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
      \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
      \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl}
    \end{align*}
  \item[(ii)] UIP propagates to $\Sigma$-types.
  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
\end{enumerate}

@@

\subsection{Intuition for our formal construction}
To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$. A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\filler$ is a filled $\framep$.
